### 2021-05-09 shared/analysis.tex

\begin{document}
	\begin{figure}
		\begin{minted}{python}
	def progam1(inpt):
		prob, _ = inpt
		z = 0
		flip = 0
		while (flip == 0):
			d = bernoulli.rvs(size=1, p=prob)[0]
			if d:
				flip = 1
			else:
				z = z + 1
		return z

	assert(z > (1 - prob)/prob)
		\end{minted}
		\caption{Program listing for finding probabilistic \texttt{assert} violation.}
	\end{figure}
	\begin{figure}
		\begin{minted}{c}
	int main()
	{
		double prob;
		int d, z = 0, flip = 0;

		make_pse_symbolic(&flip, sizeof(flip), "flip_pse_sym", 0, 1);
		make_pse_symbolic(&prob, sizeof(prob), "prob_sym", 0, 1);
		klee_make_symbolic(&z, sizeof(z), "z_sym");
		klee_assume(z >= 0);

		std::random_device rd{};
		std::mt19937 rng{rd()};
		std::bernoulli_distribution rvs(prob);

		while (flip == 0) {
			int d = rvs(rng);
			if (d) {
				flip = 1;
			} else {
				// must be executed more 
				// for the assert to pass. 
				z += 1; 
			}
		}

		return 0;
	}
		\end{minted}
		\caption{\texttt{Translate()} of the program for testing the \texttt{assert}. }
	\end{figure}
	\begin{figure}
		\begin{minted}{c}
		long long int termCount = 50000, unroll = 2500;
		while (termCount--)
		{
			flip = 0;
			z = 0;
			scanf("%Lf", &prob);

			...

			while (flip == 0 && unroll--) {
				int d = rvs(rng);
				if (d) {
					flip = 1;
				} else { 
					z += 1; 
				}
				if (z > ((double)(1 - prob) / (prob)))
					win++;
				flip_runs++;
			}
			program_runs++;
		}
		\end{minted}
		\caption{\texttt{Translate()} of the program for testing the \texttt{assert}. }
	\end{figure}
	\begin{figure}
			\begin{minted}{python}
		(flip_pse_sym <= 1),
		(0 <= flip_pse_sym),
		(prob_sym <= 1),
		(0.000001 < prob_sym),
		(0 <= z_sym),

		FAIL : (z_sym * prob_sym - (1 - prob_sym) <= 0)
		\end{minted}
		\caption{Constraints without optimization step.}
	\end{figure}
	\begin{figure}
		\begin{minted}{python}
		(flip_pse_sym <= 1),
		(0 <= flip_pse_sym),
		(prob_sym <= 1),
		(0.000001 < prob_sym),
		(0 <= z_sym),

		FAIL : (z_sym * prob_sym - (1 - prob_sym) <= 0)
		optimize : maximize(prob_sym)
		\end{minted}
		\caption{Constraints with optimization step.}
	\end{figure}
	\begin{table}
		\centering
		\caption{Comparing \texttt{prob(p)} value to cases Vs \texttt{assert} status for \texttt{optimization} over \texttt{prob} value}
		\label{}
		\begin{tabular}{ c | c | c | c | c } 
			\toprule
			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
			\hline\hline
			49999 & 50000 & 0.9999990463 & 0 & 0.0000009537 \\ \hline 
			49999 & 50000 & 0.9999995232 & 0 & 0.0000004768 \\ \hline 
			49999 & 50000 & 0.9999998808 & 0 & 0.0000001192 \\ \hline 
			49999 & 50000 & 0.9999999991 & 0 & 0.0000000009 \\ \hline 
			49999 & 50000 & 1.0000000000 & 0 & 0.0000000000 \\ \hline 
			50000 & 50000 & 0.9999847412 & 0 & 0.0000152590 \\ \hline 
			50001 & 50000 & 0.9999694825 & 0 & 0.0000305184 \\ \hline 
			50003 & 50000 & 0.9998779298 & 0 & 0.0001220851 \\ \hline 
			50008 & 50000 & 0.9997558596 & 0 & 0.0002442000 \\ \hline 
			50016 & 50000 & 0.9995117192 & 0 & 0.0004885193 \\ \hline 
			50045 & 50000 & 0.9990234385 & 0 & 0.0009775161 \\ \hline 
			50822 & 50000 & 0.9843750156 & 0 & 0.0158729998 \\ \hline 
			53303 & 50000 & 0.9375000625 & 0 & 0.0666665956 \\ \hline 
			57237 & 50000 & 0.8750001250 & 0 & 0.1428569796 \\ \hline 
			99385 & 50000 & 0.5000005000 & 0 & 0.9999980000 \\ \hline 
			\bottomrule
		\end{tabular}
	\end{table}
	\begin{table}
		\centering
		\caption{Comparing \texttt{prob(p)} value to cases where assert \texttt{\color[HTML]{CB0000} failure} occurs for \texttt{no optimization} case}
		\label{}
		\begin{tabular}{ c | c | c | c | c } 
			\toprule
			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
			\hline\hline
			49999 & 50000 & 1.0000000000 & 0 & 0.0000000000 \\ \hline 
			12798121 & 50000 & 0.0039072461 & 121 & 254.9347362328 \\ \hline 
			2118330 & 50000 & 0.0234384766 & 3 & 41.6648888947 \\ \hline 
			3191133 & 50000 & 0.0156259844 & 27 & 62.9959681516 \\ \hline 
			1592312 & 50000 & 0.0312509687 & 85 & 30.9990080819 \\ \hline 
			802573 & 50000 & 0.0625009375 & 6 & 14.9997600036 \\ \hline  
			404577 & 50000 & 0.1250008750 & 3 & 6.9999440004 \\ \hline 
			199379 & 50000 & 0.2500007500 & 2 & 2.9999880000 \\ \hline 
			133424 & 50000 & 0.3750006250 & 1 & 1.6666622222 \\ \hline 
			99661 & 50000 & 0.5000005000 & 0 & 0.9999980000 \\ \hline 
			\bottomrule
		\end{tabular}
	\end{table}
	\begin{table}
		\centering
		\caption{Comparing \texttt{prob(p)} value to cases where assert \texttt{\color[HTML]{036400} passed} without \texttt{optimization} step.}
		\label{}
		\begin{tabular}{ c | c | c | c | c } 
			\toprule
			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
			\hline\hline
			2551264 & 50000 & 0.0195322305 & 60 & 50.1974298071 \\ \hline 
			6371788 & 50000 & 0.0078134922 & 169 & 126.9837458595 \\ \hline 
			4280156 & 50000 & 0.0117197383 & 303 & 84.3261373592 \\ \hline 
			1592312 & 50000 & 0.0312509687 & 85 & 30.9990080819 \\ \hline
			266112 & 50000 & 0.1875008125 & 7 & 4.3333102223 \\ \hline 
			\bottomrule
		\end{tabular}
	\end{table}
\end{document}

>>>>

\begin{document}
	\begin{figure}
		\begin{minted}{python}

	double prob, path_prob = 1, choice_prob = 1;
	int sum = 0;

	klee_make_symbolic(&prob, f"prob_sym_{i}");
	for i in range(10):
		int d;
		klee_make_symbolic(&d, f"d_sym_{i}");

		d = bernoulli(prob);
		(d == 1) ? choice_prob = prob : choice_prob = (1 - prob);
		path_prob = path_prob * choice_prob;

		sum = sum + d;

	klee_dump(path_prob)
	klee_dump(sum) // E[heads in "n" runs] 
		\end{minted}
		\caption{Program listing for $n$ bernoulli trails experiment.}
	\end{figure}

We consider a independent $bernoulli$ trials here of flipping a fair coin "$n$" times. 
\[ 
{choice\_prob} = 
\begin{cases} 
	p & \textrm{if $d$ value is 1 corresponding to getting a "heads"} \\
	1-p & \textrm{if $d$ value is 0 corresponding to getting a "tails"}
\end{cases}
\]

for example, on the $i^{th}$ run \texttt{$\vec{d}$} can have a value.
\[
\vec{d}_{i} = encode(<0,0,0,1,1,0,1,1,1,0>)
\]

Based on the value of the $\vec{d}_{i}$, we get $w_{i}$ value using $choice\_prob$. 
\begin{equation}
	w_{i} = {(p)^{x_i} * (1-p)^{n-x_i}}
\end{equation}
where $x_i$ denotes the number of $heads$ in the $i^{th}$ randomized run and for $n$ runs. \texttt{n = 10} for the case in the above example. \\

We consider top "$k$" randomized runs now for the optimization query. The expression for \texttt{optimization} thus becomes 
\[	
	maximize(\sum_{i=1}^{k}{w_i})
\]
On substituting the value of $w_i$ from (1).
\begin{equation}	
	maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}})
\end{equation}

\begin{figure}
	\begin{equation}	
		Objective = maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}}) \mid \forall (i, j) [{x_i} \neq {x_j}]
	\end{equation}
	\caption{Optimization Expression for $k$ randomized paths}
	\label{eq:optimization-1}
\end{figure}

After performing the optimization above, we get different values of $\vec{d_i}$. For $i^{th}$ randomized run. we get a \texttt{single} one hot encoded \texttt{$\vec{d}$} vector. We show below the encoding for a few $i$ values. 
\[
\vec{d}_{1} = encode(<0,0,0,1,1,0,1,1,1,0>)
\]
\[
\vec{d}_{3} = encode(<0,1,0,1,1,0,0,0,1,0>)
\]
\[
\vec{d}_{4} = encode(<1,0,1,0,1,0,1,1,0,1>)
\]
\[
...
\]

We run the optimization by renaming the $k$ \texttt{pse} variables set appropriately and then impose the $distinct$ clause so that we don't run the optimization on the same $randomized$ runs again. \\

For best approximation of the expected value of heads in $n$ trials,
\begin{equation}	
	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i})
\end{equation}
where both $w_i$ and $sum_i$ can both be computed from the corresponding $\vec{d_i}$ expression we get from the $model$  of the $optimization$ query Eq~\ref{eq:optimization-1}

\end{document}
